Effect of quality-adjusted production function inputs

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Redoing model names.

<<Models>>=
fileName <- "ESEE2015Models.rds"
fileNameCST <- "EESE2015ModelsCST.rds"
fileNameExp <- "EESE2015ModelsExp.rds"
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(fileName)
  modelsCST <- readRDS(fileNameCST)
  modelsExp <- readRDS(fileNameExp)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.

>>>>

<<Models>>=
fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
fileNameCST <- "EcolEcon2015ModelsCST.rds"
fileNameExp <- "EcolEcon2015ModelsExp.rds"
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(fileNameCDCES)
  modelsCST <- readRDS(fileNameCST)
  modelsExp <- readRDS(fileNameExp)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.
